Making (Secure) FETCH Happen: \\ \vspace{2 mm} {\large End-to-End Metadata Security for IMAP}

### 2015-04-21 paper.tex
paper
scheduler rewrite notes

\title{Making (Secure) FETCH Happen:
\\ \vspace{2 mm} {\large Providing End-to-End Metadata Security for IMAP}}

@@

\subsection{Scheduler: Delivering from IMAP Client to IMAP Server}
The primary mechanism for limiting the amount of data the server can determine regarding message arrive metadata is a scheduling module that determines when a message should be pushed up to or pulled down from the server.

>>>>

\title{Making (Secure) FETCH Happen:
\\ \vspace{2 mm} {\large End-to-End Metadata Security for IMAP}}

@@

\subsection{Scheduler: Delivering from IMAP Client to IMAP Server}
The primary mechanism for limiting the amount of data the server can determine regarding message arrival metadata is a scheduling module that determines when a message should be pushed up to or pulled down from the server.
